Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-07-06 ProbabilisticCoherence.tex
Cleanup of simulation and conclusions

We now turn our attention to comparing different reconciliation methods in a simulation study where the data is conditionally Gaussian.  We choose the Gaussian case due to its analytical tractability which allows for evaluation on the basis of all scoring rules (including the log score).  The non-Gaussian case lies beyond the scope of this simulation study, but can be handled by a bootstrapping approach proposed in separate work.

@@

To ensure noisier disaggregate series than aggregate series, we choose $\bm{\Sigma}, \sigma^2_u$ and $\sigma^2_v$ such that
$$
\text{Var}(\varepsilon_{AA,t}+\varepsilon_{AB,t}+\varepsilon_{BA,t}+\varepsilon_{BB,t}) \le \text{Var}(\varepsilon_{AA,t}+\varepsilon_{AB,t}-v_t) \le \text{Var}(\varepsilon_{AA,t}+u_t-0.5v_t)\,,
$$
and similar inequalities hold when $\varepsilon_{AA,t}$ is replaced by $\varepsilon_{AB,t}$, $\varepsilon_{BA,t}$ and $\varepsilon_{BB,t}$ in the second and third terms.
%Therefore
%$$
%\bm{l}_1\bm{\Sigma} \bm{l}_1' \le \bm{l}_2\bm{\Sigma} \bm{l}_2' + \sigma^2_v \le  \bm{l}_3\bm{\Sigma} \bm{l}_3' + \sigma^2_u + \frac{1}{4}\sigma^2_v,
%$$
%where $\bm{l}_1 = (1,1,1,1)'$, $\bm{l}_2 = (1,1,0,0)'$ and $\bm{l}_3 = (1,0,0,0)'$, and hence
%$$\bm{l}_1\bm{\Sigma} \bm{l}_1' - \bm{l}_2\bm{\Sigma} \bm{l}_2' \le \sigma^2_v \le \frac{4}{3}(\sigma^2_u + \bm{l}_3\bm{\Sigma} \bm{l}_3' - \bm{l}_2\bm{\Sigma} \bm{l}_2').$$
The values of $\bm{\Sigma}$, $\sigma^2_u$ and $\sigma^2_v$, that we use and which satisfy these constraints are:
$\bm{\Sigma} =
\begin{pmatrix}
5.0 & 3.1 & 0.6 & 0.4 \\
3.1 & 4.0 & 0.9 & 1.4 \\
0.6 & 0.9 & 2.0 & 1.8 \\
0.4 & 1.4 & 1.8 & 3.0 \\
\end{pmatrix}$,
$\sigma^2_u = 19$ and $\sigma^2_u = 18$ in our simulation setting.

We generate data a sample size of $T=501$. Univariate ARIMA models are selected for each series using the \textit{auto.arima} function in the \textit{forecast} package \citep{hyndman2017forecasting} in R \citep{Rcore}.  The same package was used to fit each series independently using the first 500 observations, and evaluate 1-step ahead base (incoherent) probabilstic forecasts. These were then reconciled using different projections summarzied in Table~\ref{table:2}. This process was replicated using $1000$ different data sets from the same data generating processes.\todo{Are the DGPs the same in all cases?}

To assess the predictive performance of different forecasting methods, we use scoring rules as discussed in Section~\ref{sec:evaluation}. To facilitate comparisons, we report skill scores \citep{Gneiting2007}. For a given forecasting method, evaluated by a particular scoring rule $S(\cdot)$, the skill score %is calculated as
%\begin{equation}
%Ss[S_B(\cdot)] = \frac{S_B(\bm{Y},\bm{y})^{\text{ref}} - S_B(\breve{\bm{Y}},\bm{y})}{S_B(\bm{Y},\bm{y})^{\text{ref}}}\times 100\%,
%\end{equation}
%where $S_B(\cdot)$ is the average score over $B$ samples and $S_B(\bm{Y},\bm{y})^{\text{ref}}$ is the average score for the reference forecasting method. Thus $Ss[S_B(\cdot)]$ 
gives the percentage improvement of the preferred forecasting method relative to a reference method. A negative valued skill score indicates that a method is worse than the reference method, whereas any positive value indicates that method is superior to the reference method.

Table~\ref{table:3} summarizes the forecasting performance of unreconciled, bottom-up, OLS, WLS and two MinT reconciliation methods using log score, energy score and variogram score.  In all cases skill scores are calculated with the bottom-up method as reference.  All log scores are evaluated on the basis of bottom level series only, however these only differ from the log scores for the full hierarchy by a fixed constant.  The cell for log score of unreconciled forecasts is left blank since the log score is not proper in this context.  Overall, the MinT methods provide the best performance irrespective of the scoring rule, and all methods that reconcile using information at all levels of the forecast improve upon unreconciled forecasts.  Bottom up forecasts perform even worse than unreconciled forecasts.

Tables~\ref{table:4} and~\ref{table:5} break down the forecasting performance of different reconciliation methods by considering univariate scores on each individual margin. The log score and CRPS are considered while skill scores are computed with the unreconciled forecast as a reference.  When broken down in this fashion, the methods based on MinT perform best for all series and always outperform bottom up and unreconciled forecasts.  The same cannot be said for OLS which performs worse than bottom up and incoherent forecasts on every individual series\todo{Puzzling it does so bad, but outperforms unreconciled on joint evaluation}.

@@

By redefining coherent forecasts and forecast reconciliation in geometric terms we have established two new theoretical results that support the use of projections for point forecast reconciliation, and crucially have extended these concepts to probabilistic forecasting.  We show that for elliptical distributions, the true predictive density can be recovered by linear reconciliation and establish conditions for which this linear mapping is a projection.  Although this optimal projection cannot feasibly be obtained in practice, a projection similar to the MinT procedure provides a good approximation in practice.  This is supported by the results of a simulation study.  Finally, we also discuss strategies for evaluating probabilistic forecasts for hierarchical time series establishing a key results regarding the impropriety of the log score with respect to incoherent forecasts.

>>>>

We now turn our attention to comparing different reconciliation methods in a simulation study where the data is conditionally Gaussian.  We choose the Gaussian case due to its analytical tractability which allows for evaluation using all scoring rules (including the log score).  The non-Gaussian case lies beyond the scope of this simulation study, but can be handled by a bootstrapping approach proposed in separate work.

@@

To ensure noisier disaggregate series than aggregate series, we choose $\bm{\Sigma}, \sigma^2_u$ and $\sigma^2_v$ such that
$$
\text{Var}(\varepsilon_{AA,t}+\varepsilon_{AB,t}+\varepsilon_{BA,t}+\varepsilon_{BB,t}) \le \text{Var}(\varepsilon_{AA,t}+\varepsilon_{AB,t}-v_t) \le \text{Var}(\varepsilon_{AA,t}+u_t-0.5v_t)\,,
$$
and similar inequalities hold when $\varepsilon_{AA,t}$ is replaced by $\varepsilon_{AB,t}$, $\varepsilon_{BA,t}$ and $\varepsilon_{BB,t}$ in the third term.
%Therefore
%$$
%\bm{l}_1\bm{\Sigma} \bm{l}_1' \le \bm{l}_2\bm{\Sigma} \bm{l}_2' + \sigma^2_v \le  \bm{l}_3\bm{\Sigma} \bm{l}_3' + \sigma^2_u + \frac{1}{4}\sigma^2_v,
%$$
%where $\bm{l}_1 = (1,1,1,1)'$, $\bm{l}_2 = (1,1,0,0)'$ and $\bm{l}_3 = (1,0,0,0)'$, and hence
%$$\bm{l}_1\bm{\Sigma} \bm{l}_1' - \bm{l}_2\bm{\Sigma} \bm{l}_2' \le \sigma^2_v \le \frac{4}{3}(\sigma^2_u + \bm{l}_3\bm{\Sigma} \bm{l}_3' - \bm{l}_2\bm{\Sigma} \bm{l}_2').$$
The values of $\bm{\Sigma}$, $\sigma^2_u$ and $\sigma^2_v$, that we use and which satisfy these constraints are $\sigma^2_u = 19$, $\sigma^2_u = 18$ and
$$
\bm{\Sigma} =
\begin{pmatrix}
5.0 & 3.1 & 0.6 & 0.4 \\
3.1 & 4.0 & 0.9 & 1.4 \\
0.6 & 0.9 & 2.0 & 1.8 \\
0.4 & 1.4 & 1.8 & 3.0 \\
\end{pmatrix}\,.
$$

We generate data with a sample size of $T=501$. Univariate ARIMA models are selected for each series using the \textit{auto.arima} function in the \textit{forecast} package \citep{hyndman2017forecasting} in R \citep{Rcore}.  The same package was used to fit each series independently using the first 500 observations, and evaluate 1-step ahead base (incoherent) probabilistic forecasts. These were then reconciled using different projections summarised in Table~\ref{table:2}. This process was replicated using $1000$ different data sets from the same data generating processes.

To assess the predictive performance of different forecasting methods, we use scoring rules as discussed in Section~\ref{sec:evaluation}. To facilitate comparisons, we report skill scores \citep{Gneiting2007}. For a given forecasting method, evaluated by a particular scoring rule, the skill score %is calculated as
%\begin{equation}
%Ss[S_B(\cdot)] = \frac{S_B(\bm{Y},\bm{y})^{\text{ref}} - S_B(\breve{\bm{Y}},\bm{y})}{S_B(\bm{Y},\bm{y})^{\text{ref}}}\times 100\%,
%\end{equation}
%where $S_B(\cdot)$ is the average score over $B$ samples and $S_B(\bm{Y},\bm{y})^{\text{ref}}$ is the average score for the reference forecasting method. Thus $Ss[S_B(\cdot)]$ 
gives the percentage improvement of the preferred forecasting method relative to a reference method. A negative valued skill score indicates that a method is worse than the reference method, whereas any positive value indicates that method is superior to the reference method.

Table~\ref{table:3} summarizes the forecasting performance of unreconciled, bottom-up, OLS, WLS and two MinT reconciliation methods using log score, energy score and variogram score.  In all cases skill scores are calculated with the bottom-up method as reference.  All log scores are evaluated on the basis of bottom level series only, however these only differ from the log scores for the full hierarchy by a fixed constant.  The cell for log score of unreconciled forecasts is left blank since the log score is not proper in this context.  Overall, the MinT methods provide the best performance irrespective of the scoring rule, and all methods that reconcile using information at all levels of the forecast improve upon unreconciled forecasts.  Bottom up forecasts perform even worse than unreconciled forecasts in some cases.

Tables~\ref{table:4} and~\ref{table:5} break down the forecasting performance of different reconciliation methods by considering univariate scores on each individual margin. The log score and CRPS are considered while skill scores are computed with the unreconciled forecast as a reference.  When broken down in this fashion, the methods based on MinT perform best for all series and always outperform bottom up and unreconciled forecasts.

@@

By redefining coherent forecasts and forecast reconciliation in geometric terms we have established two new theoretical results that support the use of projections for point forecast reconciliation, and crucially have extended these concepts to probabilistic forecasting.  We show that for elliptical distributions, the true predictive density can be recovered by linear reconciliation and establish conditions for when this linear mapping is a projection.  Although this optimal projection cannot feasibly be obtained in practice, a projection similar to the MinT procedure provides a good approximation in practice.  This is supported by the results of a simulation study.  Finally, we also discuss strategies for evaluating probabilistic forecasts for hierarchical time series establishing a key results regarding the impropriety of the log score with respect to incoherent forecasts.
